Viscous Transport in Eroding Porous Media

### 2019-07-07 docs/transport/erosion_transport.tex
small changes to paper

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ is accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
{\color{red}
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right).
\end{align}
}
To determine if points on $\gamma_i$ are too close to the outer wall, we
use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
and that the bodies are all contained in $[-1,1] \times [-1,1]$.
Therefore, we first check if
{\color{red}
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_{\cc_i } \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out}
\end{align}
where $x_{\cc_i } $ is the x coordinate of $\cc_i$.}
If body $\gamma_i$ satisfies this condition, for each point {\color{red}$\xx=(x,y) \in
\gamma_i$}, we apply the Barycentric rule to points that satisfy
{\color{red}
\begin{align}
  \label{eqn:PointsWallCutoff}
  \|y \pm 1\| <  \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}}

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we first compute an accurate solution by using the Barycentric
quadrature rule for all discretization points.  Then, for multiple
values of $\alpha_\iin$ and $\alpha_\out$, we compute the velocity field
with the trapezoid rule for all points that do not satisfy
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that {\color{red}$\alpha_\iin = 4$ and $\alpha_\out = 4$ }give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.

>>>>

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ is accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
{\color{red}
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right).
\end{align}
}
\todo[inline]{This doesn't seem right.  $\xx$ is already on the boundary
of the jth body, so $L_j$ should not be part of the criteria.  Should be
something more like equation (44).}
To determine if points on $\gamma_i$ are too close to the outer wall, we
use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
and that the bodies are all contained in $[-1,1] \times [-1,1]$.  We
first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_{\cc_i } \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out}
\end{align}
where $x_{\cc_i } $ is the x coordinate of $\cc_i$. If body $\gamma_i$
satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
apply the Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we first compute an accurate solution by using the Barycentric
quadrature rule for all discretization points.  Then, for multiple
values of $\alpha_\iin$ and $\alpha_\out$, we compute the velocity field
with the trapezoid rule for all points that do not satisfy
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that $\alpha_\iin = 4$ and $\alpha_\out = 4$ give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.
